### 2015-03-26 Paper Seminar/isim_paper.tex
started with LP part..... a little more to come considering optimization and stuff

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{cite}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}

\begin{document}
\tableofcontents
\section{Dose-Function}
The dose-distribution within the patient's body is the accumulation of all the radiation-seeds. Therefore it is mandatory to know the radiation intensity of each seed. Equation \eqref{eq:dosefunction} shows the general approach to approximate the dose intensity function and \eqref{eq:dosefunction2} shows the used implementation of that equation.
\begin{equation}
\label{eq:dosefunction}
\dot{D}(r,\theta_{0})= S_{k}\Lambda \frac{G_{L}(r,\theta_{0})}{G_{L}(r_{0},\theta_{0})} g_{L}(r) F(r_{0},\theta_{0})
\end{equation}
\begin{equation}
\label{eq:dosefunction2}
\Rightarrow \ \dot{D}(r,\theta_{0})= S_{k}\Lambda \frac{G_{L}(r,\theta_{0})}{G_{L}(r_{0},\theta_{0})} g_{L}(r) \cdot 1
\end{equation}
\\
The following section will describe the used paramters:
\begin{description}
\item[Air-Kerma-Strength $S_{k}$]~\\
The $S_{k}$ describes the \textbf{k}inetic \textbf{e}nergy \textbf{r}eleased per unit \textbf{ma}ss called kerma. It is measured in U. Where $1\ U =1 \ \frac{cGy \cdot m^{2}}{h} $   
\item[Dose Rate Constant $\Lambda$]~\\
The dose rate constant is defined as the ratio of the dose rate at reference point $ P(r_{0},\theta_{0})  $ and the the air-kerma-strength $S_{k}$. Therefore $ \Lambda \ = \ \frac{\dot{D}(r_{0},\theta_{0})}{S_{k}} $.

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{cite}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{amssymb}

\begin{document}
\tableofcontents

\section{Model description}
HDR brachytherapy consists of several radioactive sources being placed inside the patient's body by needles. These sources will eradiate into the surrounding tissues, treating tumor cells and other critical volumes. Therefore, it relies heavily on optimal algorithms to determine the dwell times for certain, predefined goals. \\
The body is represented by an equidistant grid of voxels, defining the single body cell type. The seeds are randomly positioned within the tumor voxels. Hence, the dosis in a voxel is calculated as a sum of each seed by evaluating the dose-function up to a fixed limit, where the influence gets negligible.

\section{Dose-Function}
The dose-distribution within the patient's body is the accumulation of all the radiation-seeds. Therefore it is mandatory to know the radiation intensity of each seed. Equation \eqref{eq:dosefunction} shows the general approach to approximate the dose intensity function and \eqref{eq:dosefunction2} shows the used implementation of that equation.
\begin{equation}
\label{eq:dosefunction}
\dot{D}(r,\theta_{0})= S_{k}\Lambda \frac{G_{L}(r,\theta_{0})}{G_{L}(r_{0},\theta_{0})} g_{L}(r) F(r_{0},\theta_{0})
\end{equation}
\begin{equation}
\label{eq:dosefunction2}
\Rightarrow \ \dot{D}(r,\theta_{0})= S_{k}\Lambda \frac{G_{L}(r,\theta_{0})}{G_{L}(r_{0},\theta_{0})} g_{L}(r) \cdot 1
\end{equation}
\\
The following section will describe the used paramters:
\begin{description}
\item[Air-Kerma-Strength $S_{k}$]~\\
The $S_{k}$ describes the \textbf{k}inetic \textbf{e}nergy \textbf{r}eleased per unit \textbf{ma}ss called kerma. It is measured in U. Where $1\ U =1 \ \frac{cGy \cdot m^{2}}{h} $   
\item[Dose Rate Constant $\Lambda$]~\\
The dose rate constant is defined as the ratio of the dose rate at reference point $ P(r_{0},\theta_{0})  $ and the the air-kerma-strength $S_{k}$. Therefore $ \Lambda \ = \ \frac{\dot{D}(r_{0},\theta_{0})}{S_{k}} $.

@@

\section{Linear Programming}
In Linear Programming an objective function and constraints are used to compute the optimal solution to a minimization or maximization problem, as described in [?]. The problem consists of a certain number of variables and a feasible region, which is defined by the contraints. 
Equation \eqref{eq:LPMatrix} shows the standard form of a linear problem. The objective function, modeled with \textit{c},  is to be minimized, while the constraints, modeled with \textit{A} and \textit{b}, are satisfied. The used algorithm yields a vector x for the optimal solution.

 \begin{equation}
 \label{eq:LPMatrix}
 \begin{aligned}
 A \in \mathbb{R}^{m,n}, \ \ \ b \in \mathbb{R}^m, \ \ \ c \in \mathbb{R}^n, \ \ \ x \in \mathbb{R}^n \\
 objective function \ \ \ c^Tx = Min! \\
 min\{c^Tx|Ax \leq b, x \geq 0\}
\end{aligned}
 \end{equation}

 \subsection{Implementation}

For our problem we used CPLEX, an implementation of the simplex algorithm by IBM[?]. In simplex the feasible region is considered a polyhedron. The optimal solution must be in one of the vertices of the polyhedron. Simplex finds a start vertex and approaches the optimal solution by going on an edge from vertex to vertex, until there is no better solution.
The constraints allow us a good modelling of the tumor, since we are able to define a constraint with certain limits for each body type.

\paragraph{Basic Funtionality}
The basic functionality is depicted in algorithm \ref{alg:cplex}. This implementation checks every voxel of the body, if it is a tumor voxel or not. In case of a tumor voxel the influence of the radiation of every seed will be summed up, building a greater-equal constraint. For body voxel the influence of the radiation builds a term for the objective function. 
\begin{algorithm}
\label{alg:cplex}
 \For{x=0; x $\textless$ body.xDim; x++}{
 	\For{y=0; y $\textless$ body.yDim; y++}{
 		\For{z=0; z $\textless$ body.zDim; z++}{
			\If{$body[x][y][z].getBodyType() == tumorType$} {
				\For{i=0; i $\textless$ numberOfSeeds; i++}{
					$dosepart[i] \gets cplex.prod(dose(x,y,z,i),time[i])$	
				}
				$cplex.addGe(cplex.sum(dosepart),goalDosis(x,y,z));$
				}
			\Else{\For{i=0; i $\textless$ numberOfSeeds; i++}{
					$objective.addTerm(dose(x,y,z,i),time[i]);$	
				}

  		}
  	}
  }
  $cplex.addMinimize(objective);$\\
  $cplex.solve();$
 \caption{basic functionality}
 \end{algorithm}

\subsection{Stepwise Approach}
